{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-02-27 Paper_ttbarH_Draft.tex
KK edit: beginning of Sec. III; new diff. pdf file included as well

Before turning to a consideration of various CP-odd observables,
we remark that even though all of the above discussion took place
within the context of $gg$-initiated production, similar conclusions
are obtained for $q\qbar$-initiated production. In particular, the
definitions of the spin vectors in Eqs.~(\ref{eq3})-(\ref{eq4}) and
the general form of $d\sigma$ introduced in Eq.~(\ref{eq20}) are valid
in both cases.
%\setlength{\belowdisplayskip}{10pt} \setlength{\belowdisplayshortskip}{10pt}
%\setlength{\abovedisplayskip}{10pt} \setlength{\abovedisplayshortskip}{10pt}
\bigskip
\section{$\mathrm{\mathbf{CP}}$-odd observables}
\label{sec3}
We present below three types of observables based on the TPs discussed
in Sec.~\ref{sec2}, mean values, asymmetries and angular
distributions. These observables are sensitive not only to the
magnitude of the pseudoscalar coupling $\kpt$ but also to its
sign. With the aim of testing them, we have used in all the cases a
set of $10^5$ events $\ppprocess$ simulated at parton level with
$\mathtt{MadGraph5\_aMC@NLO}$ \cite{Madgraph} at a center-of-mass
energy of $14\,\mathrm{TeV}$ for different values of the couplings
$\kp$ and $\kpt$\footnote{Although we use the same number of events in
  all the cases, the required luminosities are different since the
  cross section depends on the value of $\kpt$.}. We have used this
somewhat large number of events with the aim of determining clearly
the extent to which the proposed observables are sensitive to the NP
coupling. However, we will discuss the corresponding experimental
viability in Sec.~\ref{sec6}. Finally, we have also imposed the
following set of cuts: $p_T$ of leptons $> 10\,\mathrm{GeV}$, $|\eta|$
of leptons $< 2.5$, $|\eta|$ of b jets $< 2.5$ and $\Delta
R_{\ell\ell}>0.4$.\par Under the assumption of no other new physics
sources but the inclusion of the pseudoscalar coupling $\kpt$,
indirect contraints based on the Higgs production from gluon fusion
followed by its decay to two photons disfavour $\kp < 0$ without
resolving the degeneracy in the sign of $\kpt$ \cite{Guadagnoli}. On
the other hand, by assuming the tensor structure of the Lagrangian to
be the same as in the SM and considering a parameterization with one
universal Higgs coupling to vector bosons, $\kappa_V$, and one
universal Higgs coupling to fermions, $\kappa_f$, the measured signal
strengths provided by ATLAS and CMS collaborations are compatible with
the values predicted by the SM, ($\kappa_f=1,\kappa_V=1$). Based on
these facts, we will set the value of the scalar coupling to its SM
value, $\kp=1$, and concentrate in modifications of the value as well
as the sign of the pseudoscalar coupling. In particular, we have
analized the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm
1$. However, we will give some results and comments regarding the pure
$\mathrm{CP}$-odd hypothesis ($\kp=0,\kpt=1$).

>>>>

Before turning to a consideration of various CP-odd observables,
we remark that even though all of the above discussion took place
within the context of $gg$-initiated production, similar conclusions
are obtained for $q\qbar$-initiated production. In particular, the
definitions of the spin vectors in Eqs.~(\ref{eq3})-(\ref{eq4}) and
the general form of $d\sigma$ introduced in Eq.~(\ref{eq20}) are valid
in both cases.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setlength{\belowdisplayskip}{10pt} \setlength{\belowdisplayshortskip}{10pt}
%\setlength{\abovedisplayskip}{10pt} \setlength{\abovedisplayshortskip}{10pt}
\bigskip
\section{$\mathrm{\mathbf{CP}}$-odd observables}
\label{sec3}
In this section we present three types of observables based on the TPs discussed
in Sec.~\ref{sec2}, namely, asymmetries, angular
distributions and mean values. These observables are sensitive not only to the
magnitude of the pseudoscalar coupling $\kpt$, but also to its
sign.  In order to test the various observables, we have
used $\mathtt{MadGraph5\_aMC@NLO}$ \cite{Madgraph} to simulate the process
$\ppprocess$ at parton level for different values of the couplings
$\kp$ and $\kpt$.  In all cases we have generated $10^5$ events
and have assumed a center-of-mass energy of
$14\,\mathrm{TeV}$.\footnote{Note that, since we generate
  the same number of events in
  each case, the corresponding integrated luminosities are different, since the
  cross section depends on the value of $\kpt$.}
We have also imposed the
following set of cuts: $p_T$ of leptons $> 10\,\mathrm{GeV}$, $|\eta|$
of leptons $< 2.5$, $|\eta|$ of b jets $< 2.5$ and $\Delta
R_{\ell\ell}>0.4$.  Note that we have used this
somewhat large number of events ($10^5$) in order to determine clearly
the extent to which the proposed observables are sensitive to the NP
coupling.  Section~\ref{sec6} contains an
analysis of the experimental feasibility of the more promising observables.
{\bf (KK: I may not have worded this quite correctly.)}

Before continuing on to our analysis, let us make a few comments
regarding the values that we choose for $\kp$ and $\kpt$.
First of all, we note that if the pseudoscalar
coupling $\kpt$ is the only source of physics beyond the SM,
then indirect contraints (based on Higgs production via gluon fusion,
followed by Higgs decay to two photons {\bf (KK: can we just say
  something like $gg\to H \to \gamma\gamma$?  Or is that not
  correct?)}) disfavour $\kp < 0$ but do not
resolve the degeneracy {\bf (KK: did I reword this correctly?)}
in the sign of $\kpt$ \cite{Guadagnoli}. On
the other hand, if one assumes that the tensor structure of the
Higgs interactions are the
same as those of the SM and if one parameterizes these interactions via
one universal Higgs coupling to vector bosons, $\kappa_V$, and one
universal Higgs coupling to fermions, $\kappa_f$, then the measured signal
strengths provided by the ATLAS and CMS collaborations are compatible with
the values predicted by the SM, (namely, $\kappa_f=1$ and $\kappa_V=1$).
With these facts in mind, we will, for the most part,
set the value of the scalar coupling to its SM
value ($\kp=1$) and will allow the pseudoscalar coupling to take on
various values (including both possible signs). In particular, we
analyze the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm 1$.
In addition, we also provide some analysis regarding the pure
$\mathrm{CP}$-odd case ($\kp=0,\kpt=1$).
